Working title: Ecological network control

### 2018-06-13 paper/manuscript.Rmd
Advances in text for results section

@@

@@

>>>>

```{r correlation-calculations}
drake::loadd(sl_char_corr)
correlations <- sl_char_corr %>% 
  extract2("mean") %>%
  as.data.frame() %>%
  tibble::rownames_to_column() %>%
  dplyr::filter(!rowname %in% c("control_capacity", "superior"))
```

The control capacity $\phi$ and the likelihood of being a superior node $\sigma$ are weakly correlated with commonly used centrality metrics. 
Specifically, the correlation coefficient between the control capacity $\phi$ and other metrics ranged between `r round(min(correlations$control_capacity), 2)` and `r round(max(correlations$control_capacity), 2)` while the correlation coefficient between the likelyhood of being a superior node $\sigma$ and the centrality metrics ranged between `r round(min(correlations$superior), 2)` and `r round(max(correlations$superior), 2)` (Figure \@ref(fig:fig-correlogram)).

@@

Both plants and pollinators were distributed across a gradient of control capacity and wether they were superior nodes or not (Figure \@ref(fig:fig-species-level)). 
This distribution, in particular for control capacity, was independent of the degree of species. 
Remarkably, every single invasive plant species in our dataset had both the maximum control capacity and was classified as a superior node.

@@

The model that best explained Although a species control capacity was not correlated to any of the centrality metrics, we found that it was a strong correlation w  Control capacity was strongly related to the nested
